\chapter{Related Work}

TODO: Introduction for this section. 

\section{Reducing the burden of self tracking}
Self tracking can solve the problem of memory recall bias, by letting the user register observation in the moment (or very close to) they occur. But requiring the user to log observation introduces a burden of the work involved in doing so. As mention traditionally this has been done with pen and paper, but with the invention of smartphones and smartwatches this burden can be reduces. The work of Ponnada et al., 2017 \cite{compare} investigate the interruption burden for with both smartphones and smartwatches when used to with both regular EMA and $\mu$EMA. The difference between EMA and $\mu$EMA is that EMA will prompt the use less than $\mu$EMA, but requires the user to answer several questions back to back, where $\mu$EMA will instead prompt the user much more frequently, but only require the user to answer one question, which can be answered on the same screen showing the question. 


In a prior 4 week pilot study Ponnada et al., 2017 found that smartwatch $\mu$EMA demonstrated higher response rates and participants reported a lower percieved burden than smartphone EMA, even though the interruption rate for smartwatch $\mu$EMA was 8 times higher than smartphone EMA. In a new 4 week study they gathered data based on a smartwatch EMA in order to determine if the previous result where due to the fact that the data was gathered on a watch, or if it in fact was due to the $\mu$EMA. Their results showed that there were no statistically significant differences in compliance, completion, and first-prompt response rates observed between smartphone EMA and smartwatch EMA. But smartwatch $\mu$EMA response rates where significantly higher than smartwatch EMA. They suggest that 

\section{Ponnada et al., 2017}

\cite{compare}


\section{Larsen et al., 2017}
\cite{eg}

\section{Dam-Jensen, 2018}
\cite{dam}

\section{Kami\'nski, 2016}
\cite{tomas}


\section{Matejka et al., 2016}
\cite{grey}

\section{Borg and Bord, 1991}
\cite{borg}